Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-16 prop_letter.tex
prop_letter.tex Fix a citation...

Our generalization of quantum probability measures to QIVPMs will
allow us to strengthen one of the fundamental theorems in of quantum
information: the Kochen-Specker
theorem~\cite{PeresRon1988,peres1995quantum}. Our stronger version of
the theorem will suggest a resolution to the debate initiated by Meyer
and Mermin on the relevance of the Kochen-Specker to experimental, and
hence finite-precision, quantum
measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
. Specifically, the original Kochen-Specker theorem is formulated
under the assumption that all observables of a quantum mechanical
system have \emph{definite values at all
  times}~\cite{StanfordXXX}. Our interval-valued framework will allow
us to state, and prove, a stronger version of the theorem that holds
even if the observables have values that are only definite up to some
specific parameter that quantifies experimental uncertainty. Put
differently, our stronger statement and theorem quantifies Mermin's
qualitative argument:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case~\citep{Mermin1999}.
\end{quote}

>>>>

Our generalization of quantum probability measures to QIVPMs will
allow us to strengthen one of the fundamental theorems in of quantum
information: the Kochen-Specker
theorem~\cite{PeresRon1988,peres1995quantum}. Our stronger version of
the theorem will suggest a resolution to the debate initiated by Meyer
and Mermin on the relevance of the Kochen-Specker to experimental, and
hence finite-precision, quantum
measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
. Specifically, the original Kochen-Specker theorem is formulated
under the assumption that all observables of a quantum mechanical
system have \emph{definite values at all
  times}~\cite{Held2016}. Our interval-valued framework will allow
us to state, and prove, a stronger version of the theorem that holds
even if the observables have values that are only definite up to some
specific parameter that quantifies experimental uncertainty. Put
differently, our stronger statement and theorem quantifies Mermin's
qualitative argument:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case~\citep{Mermin1999}.
\end{quote}
